---
title: "PlotCodeChunks"
output: html_document
---

This markdown document contains code chunks for graphics and tables that will be included in the RShiny dashboard. These will have to be altered with dynamic variables to reflect interactive selections which will, for now, be hardcoded
```{r}
if(!require(tidyverse)){install.packages("tidyverse")}
if(!require(DT)){install.packages("DT")}
if(!require(sf)){install.packages("sf")}
if(!require(leaflet)){install.packages("leaflet")}
if(!require(tigris)){install.packages("tigris")}

load(file = file.path(getwd(), "data", "immunodata.RData"))




```


Overall Rates of Vaccination Waivers through the state

*Dropdown that selects between "Vaccinated", "Waiver", "Medical Waiver", Religious Waiver", "Philosophical Waivers
*Selector that selects between Kindergarten, 7th Grade, or All
*Selector for % vs Count
This one will be using overall df, so colnames from grade selection will not be used, rather group will be used

```{r}

vaxSelections <- c("Complete for Recommended Vaccines" = "COMP", "Vaccination Waiver (Any)" = "Waiver", "Medical Waiver" = "Medical", "Religious Waiver" = "Religious", "Philosophical Waiver" = "Philosophical")
gradeSelection <- c("Kindergarten" = "K", "7th Grade" = "7", "Overall" = "tot")
tallySelection <- c("Percent (%)" = "pct", "Count (N)" = "n")

chosenVax <- "Religious"
chosenGrade <- "7"
chosenTally <- "pct"

coi <- paste0(chosenTally, chosenVax)
dat <- df %>%
  filter(Group %in% chosenGrade) %>%
  select(all_of(c("NAME", "DISTRICT", "COUNTY", coi)))

datatable(dat) #find a way to change colname to a presentable column name

#Create a table/plot by county for all the state + corresponding map
coiCounty <- paste0(chosenGrade,"_",chosenTally,chosenVax)
datCounty <- dfCounty %>%
  select(all_of(c("COUNTY", "val" = coiCounty)))

#Make map of tables
mi_counties <- counties(state = "MI", cb = TRUE, year = 2024, class = "sf")
mapdat <- left_join(mi_counties, datCounty, by = c("NAME" = "COUNTY"))
mapdat
pal <- colorNumeric("YlOrRd", domain = mapdat$val, na.color = "#f0f0f0")

#will have to be renderLeaflet instead in shinyDash
mi_map <- leaflet(mapdat) %>%
  addProviderTiles("CartoDB.Positron") %>%
  addPolygons(
    fillColor = ~pal(val),
    fillOpacity = 0.8, weight = 1, color = "white",
    label = ~paste(NAME, "Rate: ", round(val, 1)),
    highlightOptions = highlightOptions(weight = 2, color = "blue", bringToFront = TRUE)) %>%
  addLegend(
    pal = pal,
    values = mapdat$val,
    title = "{VALUE} (pct/n)",
    position = "bottomright"
  )

mi_map


```

Within-County Data

Within a specified county:
**ADDED CHOICE OF COUNTY, other inputs the same

Take a county, display table and histogram of schools 
```{r}

countyChoice <- "Oakland"

analytic <- df %>%
  filter(COUNTY == countyChoice) %>%
  select(all_of(c("NAME", "DISTRICT", "COUNTY", coi)))

datatable(analytic)

analytic %>%
ggplot(aes(x = fct_relevel(.data$DISTRICT, .data[[coi]]), y = .data[[coi]])) +
  geom_col() +
  coord_flip()


```


